---
title: "p8105_hw6_qs2261"
author: "Qinting Shen"
date: "2023-11-27"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(modelr)
```


## Problem 3

### Load and clean the data for regression analysis

Import data
```{r}
birthweight_raw = 
  read_csv(file = 'birthweight.csv')
```

Check for missing value
```{r}
birthweight_raw |> 
  summarise_all(~sum(is.na(.)))
```
No missing value???

Clean data
```{r}
birthweight_df = 
  birthweight_raw|> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
    )
```

### Propose a regression model for birthweight
```{r}
fit = lm(bwt ~babysex + bhead + blength + delwt + fincome + frace +
               gaweeks + malform + menarche + mheight + momage + mrace +
               parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,
             data = birthweight_df) 

broom::glance(fit)
broom::tidy(fit)
```
I put all the variables into my regression model.

### Diagnostics
```{r}
birthweight_df |> 
  modelr::add_predictions(fit) |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```
The pattern of scatter plot between predictions and residuals is not random



new try
```{r}
fit2 = lm(bwt ~babysex + bhead + blength + delwt + gaweeks + wtgain,
             data = birthweight_df)

broom::glance(fit2)
broom::tidy(fit2)
```

```{r}
birthweight_df |> 
  modelr::add_predictions(fit2) |> 
  modelr::add_residuals(fit2) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```




### Compare my model to two others:

* One using length at birth and gestational age as predictors (main effects only)

```{r}
main_effects = lm(bwt ~ blength + gaweeks ,
             data = birthweight_df) 

broom::glance(main_effects)
broom::tidy(main_effects)

anova(main_effects, fit) |> 
  broom::tidy()
```


* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
three_way = lm(bwt ~ bhead * blength * babysex ,
             data = birthweight_df) 

broom::glance(three_way)
broom::tidy(three_way)

anova(three_way, fit) |> 
  broom::tidy()
```


```{r}
cv_df_compare = 
  crossv_mc(birthweight_df, 100)
```


```{r}
cv_df = 
  cv_df_compare |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) |> 
  mutate(
    fit_mod = map(.x = train, ~lm(bwt ~babysex + bhead + blength + delwt + fincome + frace +gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = .x)),
    main_effects_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction_mod = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) |> 
    mutate(
    rmse_fit = map2_dbl(.x = fit_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_main_effects = map2_dbl(.x = main_effects_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(.x = interaction_mod, .y = test, ~rmse(model = .x, data = .y))
    ) |> 
  select(-fit_mod, -main_effects_mod, -interaction_mod)
```

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

By looking at the violin plot, I found the RMSE in my model is smallest, followed by interaction model.
