---
title: "p8105_hw6_qs2261"
author: "Qinting Shen"
date: "2023-11-27"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(modelr)
```

## Problem 2

### Load theCentral Park weather data 
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```


### bootstrap
produce estimates of r̂ 2 and log(β̂ 1∗β̂ 2)
```{r}
r_square =
  bootstrap(weather_df, 5000, id = "strap_number") |> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::glance)
  ) |> 
  select(strap_number, results) |> 
  unnest(results) |> 
  select(strap_number, r.squared)

log_beta = 
  bootstrap(weather_df, 5000, id = "strap_number") |> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::tidy)
  ) |> 
  select(strap_number, results) |> 
  unnest(results) |> 
  select(strap_number, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  mutate(
    log_beta1_beta2 = log(tmin*prcp)
  )
```
* There are many estimates of prcp is negative, so we get many NAs when calculating the log(beta1*beta2).


Plot the distribution of your estimates, and describe these in words.
```{r}
r_square |> 
  ggplot(aes(x = r.squared))+
  geom_density()
```

* r_square: the distribution of r_square under repeated strap is a little left skewed, the majority of the r square value is greater than 0.9 and centered around 0.918.

```{r}
log_beta |> 
  ggplot(aes(x = log_beta1_beta2))+
  geom_density()
```

* log_beta: Since we get many NAs when calculating the log(beta1*beta2), we removed 3327 rows in this distribution plot. The distribution of log_beta under repeated strap is left skewed, and the majority estimates of the log_beta are greater than -7.5 and centered around -5.

Compute 95% CI
```{r}
r_square |> 
  summarize(
    ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975)
  )

log_beta |> 
  summarize(
    ci_lower = quantile(log_beta1_beta2, 0.025, na.rm = TRUE),
    ci_upper = quantile(log_beta1_beta2, 0.975, na.rm = TRUE)
  )
```


## Problem 3

### Load and clean the data for regression analysis

Import data
```{r}
birthweight_raw = 
  read_csv(file = 'birthweight.csv')
```

Check for missing value
```{r}
birthweight_raw |> 
  summarise_all(~sum(is.na(.)))
```


Clean data
```{r}
birthweight_df = 
  birthweight_raw|> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
    )
```

### Propose a regression model for birthweight
```{r}
fit = lm(bwt ~babysex + bhead + blength + delwt + fincome + frace +
               gaweeks + malform + menarche + mheight + momage + mrace +
               parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,
             data = birthweight_df) 

broom::glance(fit)
broom::tidy(fit)
```
* I put all the variables into my regression model since all the variables have potential to affect birth weight.

### Diagnostics
```{r}
birthweight_df |> 
  modelr::add_predictions(fit) |> 
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```
* The pattern of scatter plot between predictions and residuals is not random


### Compare my model to two others:

One using length at birth and gestational age as predictors (main effects only)

```{r}
main_effects = lm(bwt ~ blength + gaweeks ,
             data = birthweight_df) 

broom::glance(main_effects)
broom::tidy(main_effects)

anova(main_effects, fit) |> 
  broom::tidy()
```


One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
three_way = lm(bwt ~ bhead * blength * babysex ,
             data = birthweight_df) 

broom::glance(three_way)
broom::tidy(three_way)

anova(three_way, fit) |> 
  broom::tidy()
```

### Cross-validate
```{r}
cv_df_compare = 
  crossv_mc(birthweight_df, 100)
```


```{r}
cv_df = 
  cv_df_compare |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) |> 
  mutate(
    fit_mod = map(.x = train, ~lm(bwt ~babysex + bhead + blength + delwt + fincome + frace +gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = .x)),
    main_effects_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction_mod = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) |> 
    mutate(
    rmse_fit = map2_dbl(.x = fit_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_main_effects = map2_dbl(.x = main_effects_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(.x = interaction_mod, .y = test, ~rmse(model = .x, data = .y))
    ) |> 
  select(-fit_mod, -main_effects_mod, -interaction_mod)
```

compare rmse
```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

* By looking at the violin plot, I found the RMSE in my model is smallest, followed by interaction model. 

* It might be better to use my model to predict the birthweight but not investigate the relationship between these exposures and birthweight since I simply put all the relavent variables into the model. Additionally, the difference of rmse between interaction model and my model is not that big. Therefore, I think interaction model is better here.
